Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-01-22 WSSSPE3/report/wg_appendix_software_credit.tex
Small changes to Software Credit working group
* Use my full name
* clarify description of Mozilla Science's Contributorship Badges for Science & relationship with Project CRediT
* Codemeta -> CodeMeta

\begin{itemize}
\item Alice Allen -- Astrophysics Source Code Library
\item Sou-Cheng Choi -- NORC at University of Chicago, Illinois Institute of Technology
\item James Hetherington -- University College London
\item Lorraine Hwang -- University of California, Davis
\item Daniel S.\ Katz -- University of Chicago, Argonne National Laboratory
\item Frank L\"{o}ffler -- Louisiana State University
\item Abby Cabunoc Mayes -- Mozilla Science Lab
\item Kyle E.\ Niemeyer -- Oregon State University
\item Grace Peng -- National Center for Atmospheric Research
\item Ilian Todorov -- Science \& Technology Facilities Council, UK
\end{itemize}

@@

\item Mozilla Science Lab's recently introduced Contributorship Badges for
Science~\cite{Mozilla_badges}, which provide a badge---associated with
ORCID~\cite{orcid}---based on author contributions in a similar manner to
Project CRediT.

@@

At a minimum, the metadata needed for software citation %(aside from the DOI for
%the software itself) \choinote{DOI is in the list below}
includes:
\begin{itemize}
    \item Name of software,
    \item DOI for software,
    \item Contributors, in the form of names and ORCIDs,
    \item Software dependencies, in the form of DOIs, and
    \item Other people and artifacts that would be cited or acknowledged in a paper.
\end{itemize}
This information would then be contained in a citation file, e.g., as part of
the GitHub repository. The group also discussed similar efforts such as
Codemeta\footnote{Codemeta: \url{https://github.com/codemeta/codemeta}}, an
attempt to codify minimal metadata schemes in JSON and XML for scientific
software and code, and implementing transitive credit via
JSON-LD~\cite{wssspe2_katz}. Some questions arose about how this information
would be stored for closed-source software.

@@

Although this working group's discussions at WSSSPE3 did not focus much on the
topic of tenure and professional advancement, 
%we should recognized that this problem goes beyond faculty to recognizing the role of "Research Software Engineers"
the group recognized that there is no standard
policy---generally even within a single university---for software products to be
included in promotion and tenure dossiers. Thus, it may be difficult to
encourage valuing software contributions across the United States or United
Kingdom and globally; furthermore, stakeholders are typically not tenured and
thus may not be influential enough to change the status quo.

>>>>

\begin{itemize}
\item Alice Allen -- Astrophysics Source Code Library
\item Sou-Cheng Choi -- NORC at University of Chicago, Illinois Institute of Technology
\item James Hetherington -- University College London
\item Lorraine Hwang -- University of California, Davis
\item Daniel S.\ Katz -- University of Chicago, Argonne National Laboratory
\item Frank L\"{o}ffler -- Louisiana State University
\item Abigail Cabunoc Mayes -- Mozilla Science Lab
\item Kyle E.\ Niemeyer -- Oregon State University
\item Grace Peng -- National Center for Atmospheric Research
\item Ilian Todorov -- Science \& Technology Facilities Council, UK
\end{itemize}

@@

\item Mozilla Science Lab's recently introduced Contributorship Badges for
Science~\cite{Mozilla_badges}, which provide a badge---associated with
ORCID~\cite{orcid}---for author contributions based on the taxonomy
outlined in Project CRediT.

@@

At a minimum, the metadata needed for software citation %(aside from the DOI for
%the software itself) \choinote{DOI is in the list below}
includes:
\begin{itemize}
    \item Name of software,
    \item DOI for software,
    \item Contributors, in the form of names and ORCIDs,
    \item Software dependencies, in the form of DOIs, and
    \item Other people and artifacts that would be cited or acknowledged in a paper.
\end{itemize}
This information would then be contained in a citation file, e.g., as part of
the GitHub repository. The group also discussed similar efforts such as
CodeMeta\footnote{CodeMeta: \url{https://github.com/codemeta/codemeta}}, an
attempt to codify minimal metadata schemes in JSON and XML for scientific
software and code, and implementing transitive credit via
JSON-LD~\cite{wssspe2_katz}. Some questions arose about how this information
would be stored for closed-source software.

@@

Although this working group's discussions at WSSSPE3 did not focus much on the
topic of tenure and professional advancement, 
%we should recognized that this problem goes beyond faculty to recognizing the role of ``Research Software Engineers''
the group recognized that there is no standard
policy---generally even within a single university---for software products to be
included in promotion and tenure dossiers. Thus, it may be difficult to
encourage valuing software contributions across the United States or United
Kingdom and globally; furthermore, stakeholders are typically not tenured and
thus may not be influential enough to change the status quo.
However, as discussed in Section~\ref{RSE}, this is changing for Research Software Engineers, at least in the UK.
